---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package help you to import and manage fars data.


First of all we have to install and load the package 

```{r}
# install.package("devtools")
# devtools::install_github("CorradoLanera/weektwo")
library(weektwo)
```



## Import basic files
To import fars with the `weektwo` package, you can simply provide the
full path to your file and call `fars_read()`. In the package, there are
same sample data in the `sample-data` folder of the package.

Hence, we can take advantage the test files to provide some examples

```{r}
file_path  <- system.file("sample-data", package = "weektwo")
fars_files <- list.files(file_path, "\\.bz2$")

example_fars <- file.path(file_path, fars_files[[1]])

example_fars

fars_read(example_fars)
```



Anyway you can load more than one file just providing its data, and the
path to the folder in wich the files are stored.

```{r}
list_of_faers <- fars_read_years(c(2013, 2014), path = file_path)
list_of_faers
```

The output is a named list, hance we can access to each element by the
double square brackets (`[[`) both using index or the year itself (as
a string).

```{r}
by_index <- list_of_faers[[1]]
by_name <- list_of_faers[["2013"]]

identical(by_index, by_name)

by_name
```


If you want to compare the distribution of fars among multiple year
you can directly access to the number of fars each month on the years
of your interest. This is as simple as a single funciton call

```{r}
fars_summarize_years(c(2013, 2014), path = file_path)
```

At the end the `weektwo` package let you able to map the fars among
countries. Let pass to `fars_map_state()` an ID of a cuntry and you are 
ready to go!

```{r}
fars_map_state(
    state = 1,
    year  = 2013,
    path  = file_path
)
```

